Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

It can be concluded that the algorithm has not been able to determine whether the regression
occurs due to changes that occur at the application level or changes
that occur outside the application such as an increase in the number of users or an increase in
load on some operations. However, if from the critical path analysis result can be seen the difference
latency of operations that exceed a certain threshold can be an indication that
regression that occurs is caused by changes at the application level. On the other hand, if
critical path analysis cannot determine which operation is a candidate cause
regression because the difference is not greater than the threshold, it can be
indication that the detected regression is due to changes caused by
by external factors.

>>>>

It can be concluded that the algorithm has not been able to determine whether the regression
occurs due to changes that occur at the application level or changes
that occur outside the application such as an increase in the number of users or an increase in
load on some operations. However, if from the critical path analysis result can be seen the difference
latency of operations that exceed a certain threshold can be an indication that
regression that occurs is caused by changes at the application level. On the other hand, if
critical path analysis cannot determine which operation is a candidate that causes
regression because the difference is not greater than the threshold, it can be and
indication that the detected regression is due to changes caused by
by external factors.
